\vspace{5em}On Evaluating Adversarial Robustness

### 2019-04-25 paper.tex
comments on number of iterations as a non-measure of robustness, verifying convergence of the adversarial loss, and the use of random restarts

@@

\begin{itemize}[leftmargin=*]
  \item \S\ref{sec:pleaseactuallythink} \textbf{Do not mindlessly follow this list}; make sure to still think about the evaluation.
\item \S\ref{sec:threatmodel} \textbf{State a precise threat model} that the defense is supposed to be effective under.
  \begin{itemize}[leftmargin=*]
  \item The threat model assumes the attacker knows how the defense works.
  \item The threat model states attacker's goals, knowledge and capabilities.
  \item For security-justified defenses, the threat model realistically models some adversary.
  \item For worst-case randomized defenses, the threat model captures the perturbation space.
  \item Think carefully and justify any $\ell_p$ bounds placed on the adversary.
  \end{itemize}
\item \S\ref{sec:adaptive} Perform \textbf{adaptive attacks} to give an upper bound of robustness.
  \begin{itemize}[leftmargin=*]
  \item The attacks are given access to the full defense, end-to-end.
  \item The loss function is changed as appropriate to cause misclassification.
  \item \S\ref{sec:whichattack} \textbf{Focus on the strongest attacks} for the threat model and defense considered.
  \end{itemize}
\item \S\ref{sec:releasecode} Release \textbf{pre-trained models and source code}.
  \begin{itemize}[leftmargin=*]
  \item Include a clear installation guide, including all dependencies.
  \item There is a one-line script which will classify an input example with the defense.
  \end{itemize}
\item \S\ref{sec:cleanaccuracy} Report \textbf{clean model accuracy} when not under attack.
  \begin{itemize}[leftmargin=*]
  \item For defenses that abstain or reject inputs, generate a ROC curve.
  \end{itemize}
\item \S\ref{sec:sanitycheck} Perform \textbf{basic sanity tests} on attack success rates.
  \begin{itemize}[leftmargin=*]
    \item Verify iterative attacks perform better than single-step attacks.
    \item Verify increasing the perturbation budget strictly increases attack success rate.
    \item With ``high'' distortion, model accuracy should reach levels of random guessing.% or even drop to zero.
  \end{itemize}
\item \S\ref{sec:100success} Generate an \textbf{attack success rate vs. perturbation budget} curve.
  \begin{itemize}[leftmargin=*]
  \item Verify the x-axis extends so that attacks eventually reach 100\% success.
  \item For unbounded attacks, report distortion and not success rate.
  \end{itemize}
\item \S\ref{sec:whitebox} Verify \textbf{adaptive attacks} perform better than any other.
  \begin{itemize}[leftmargin=*]
  \item Compare success rate on a per-example basis, rather than averaged across the dataset.
  \item Evaluate against some combination of black-box, transfer, and random-noise attacks.
  \end{itemize}
\item \S\ref{sec:describeattacks} Describe the \textbf{attacks applied}, including all hyperparameters.

@@

\begin{itemize}[leftmargin=*]
\item \S\ref{sec:whichattack} Apply a \textbf{diverse set of attacks} (especially when training on one attack approach).
  \begin{itemize}[leftmargin=*]
  \item Do not blindly apply multiple (nearly-identical) attack approaches.
  \end{itemize}
\item \S\ref{sec:gradientfree} Try at least one \textbf{gradient-free attack} and one \textbf{hard-label attack}.
  \begin{itemize}[leftmargin=*]
  \item Try \cite{chen2017zoo,uesato2018adversarial,ilyas2018black,brendel2017decision}.
  \item Check that the gradient-free attacks succeed less often than gradient-based attacks.
  \item Carefully investigate attack hyperparameters that affect success rate.
  \end{itemize}
\item \S\ref{sec:transfer} Perform a \textbf{transferability attack} using a similar substitute model.
  \begin{itemize}[leftmargin=*]
    \item Select a substitute model as similar to the defended model as possible.
    \item Generate adversarial examples that are initially assigned high confidence.
    \item Check that the transfer attack succeeds less often than white-box attacks.
  \end{itemize}
\item \S\ref{sec:eot} For randomized defenses, properly \textbf{ensemble over randomness}.
  \begin{itemize}[leftmargin=*]
  \item Verify that attacks succeed if randomness is assigned to one fixed value.
  \item State any assumptions about adversary knowledge of randomness in the threat model.
  \end{itemize}
\item \S\ref{sec:bpda} For non-differentiable components, \textbf{apply differentiable techniques}.
  \begin{itemize}[leftmargin=*]
  \item Discuss why non-differentiable components were necessary.
  \item Verify attacks succeed on undefended model with those non-differentiable components.
  \item Consider applying BPDA~\citep{athalye2018obfuscated} if applicable.
  \end{itemize}
\item \S\ref{sec:converge} Verify that the \textbf{attacks have converged} under the selected hyperparameters.
  \begin{itemize}[leftmargin=*]
  \item Verify that doubling the number of iterations does not increase attack success rate.
  \item Plot attack effectiveness versus the number of iterations.
  \item Explore different choices of the step size or other attack hyperparameters.
  \end{itemize}
\item \S\ref{sec:hyperparams} Carefully \textbf{investigate attack hyperparameters} and report those selected.
  \begin{itemize}[leftmargin=*]
  \item Start search for adversarial examples at a random offset.
  \item Investigate if attack results are sensitive to any other hyperparameters.
  \end{itemize}
  \item \S\ref{sec:priorwork} \textbf{Compare against prior work} and explain important differences.
  \begin{itemize}[leftmargin=*]
  \item When contradicting prior work, clearly explain why differences occur.
  \item Attempt attacks that are similar to those that defeated previous similar defenses.
  \item When comparing against prior work, ensure it has not been broken.
  \end{itemize}
\item \S\ref{sec:generalrobustness} Test \textbf{broader threat models} when proposing general defenses. For images:
  \begin{itemize}[leftmargin=*]
  \item Apply rotations and translations \citep{engstrom2017rotation}.
  \item Apply common corruptions and perturbations \citep{hendrycks2018benchmarking}.
  \item Add Gaussian noise of increasingly large standard deviation \citep{ford2019adversarial}.
  \end{itemize}

@@

On at least a few inputs, confirm
that the number of iterations of gradient descent being performed is
sufficient by plotting the attack success versus the number of
iterations.
%
This plot should eventually plateau; if not, the attack
has not converged and more iterations can be used until
it does.
%
The number of
iterations necessary is generally inversely proportional to step size and
proportional to distortion allowed.
%
Dataset complexity is often related.

@@

There are few reasonable threat models under which an attacker can
compute 100 iterations of gradient descent, but not 1000.
%
Because the threat model must not constrain the approach an
attacker takes, it is worth evaluating against a strong attack
with many iterations of gradient descent.

\paragraph{Ensure doubling attack iterations does not increase attack success rate.}
%
Because choosing any fixed bounded number of iterations can be difficult to
generalize, one simple and useful method for determining if ``enough'' iterations
have been performed is to try doubling the number of iterations and check if this
improves on the adversarial examples generated.
%
This single test is not the only method to select the number of iterations,
but once some value has been selected, doubling the number of iterations
can be a useful test that the number selected is probably sufficient.

@@

\paragraph{Start search from random offsets.}
%
When performing iterative attacks,
it is useful to begin the search for adversarial examples at random
offsets away from the initial, source input.
%
This can reduce the
distortion required to generate adversarial examples by 10\%
\citep{carlini2017towards}, and help avoid causing gradient masking
\citep{tramer2017ensemble,madry2017towards}.
%
Doing this
every time is not necessary, but doing it at least once to verify it
does not significantly change results is worthwhile.
%
Prior work has found that using at least 10 random starting points is effective.

@@

>>>>

It is customary for defenses not to impose any computational bounds on an attacker (i.e., the above definitions of adversarial risk consider only the \emph{existence} of adversarial examples, and not the difficulty of finding them). We believe that restricting an adversary's computational power would only be interesting if we could base robustness on a cryptographic assumption (e.g., the model is robust under the assumption that the adversary cannot factor a product of large primes). We are not aware of any defense that achieves this. Stronger restrictions (e.g., the adversary is limited to attacks with $100$ iterations) are typically uninteresting in that they cannot be meaningfully enforced and there is usually no economic reason for an adversary not to spend a little more time to succeed.

@@

\begin{itemize}[leftmargin=*]
  \item \S\ref{sec:pleaseactuallythink} \textbf{Do not mindlessly follow this list}; make sure to still think about the evaluation.
\item \S\ref{sec:threatmodel} \textbf{State a precise threat model} that the defense is supposed to be effective under.
  \begin{itemize}[leftmargin=*]
  \item The threat model assumes the attacker knows how the defense works.
  \item The threat model states attacker's goals, knowledge and capabilities.
  \item For security-justified defenses, the threat model realistically models some adversary.
  \item For worst-case randomized defenses, the threat model captures the perturbation space.
  \item Think carefully and justify any $\ell_p$ bounds placed on the adversary.
  \end{itemize}
\item \S\ref{sec:adaptive} Perform \textbf{adaptive attacks} to give an upper bound of robustness.
  \begin{itemize}[leftmargin=*]
  \item The attacks are given access to the full defense, end-to-end.
  \item The loss function is changed as appropriate to cause misclassification.
  \item \S\ref{sec:whichattack} \textbf{Focus on the strongest attacks} for the threat model and defense considered.
  \end{itemize}
\item \S\ref{sec:releasecode} Release \textbf{pre-trained models and source code}.
  \begin{itemize}[leftmargin=*]
  \item Include a clear installation guide, including all dependencies.
  \item There is a one-line script which will classify an input example with the defense.
  \end{itemize}
\item \S\ref{sec:cleanaccuracy} Report \textbf{clean model accuracy} when not under attack.
  \begin{itemize}[leftmargin=*]
  \item For defenses that abstain or reject inputs, generate a ROC curve.
  \end{itemize}
\item \S\ref{sec:sanitycheck} Perform \textbf{basic sanity tests} on attack success rates.
  \begin{itemize}[leftmargin=*]
    \item Verify iterative attacks perform better than single-step attacks.
    \item Verify that iterative-attacks use sufficient iterations and random restarts to converge. 
    \item Verify increasing the perturbation budget strictly increases attack success rate.
    \item With ``high'' distortion, model accuracy should reach levels of random guessing.% or even drop to zero.
  \end{itemize}
\item \S\ref{sec:100success} Generate an \textbf{attack success rate vs. perturbation budget} curve.
  \begin{itemize}[leftmargin=*]
  \item Verify the x-axis extends so that attacks eventually reach 100\% success.
  \item For unbounded attacks, report distortion and not success rate.
  \end{itemize}
\item \S\ref{sec:whitebox} Verify \textbf{adaptive attacks} perform better than any other.
  \begin{itemize}[leftmargin=*]
  \item Compare success rate on a per-example basis, rather than averaged across the dataset.
  \item Evaluate against some combination of black-box, transfer, and random-noise attacks.
  \end{itemize}
\item \S\ref{sec:describeattacks} Describe the \textbf{attacks applied}, including all hyperparameters.

@@

\begin{itemize}[leftmargin=*]
\item \S\ref{sec:whichattack} Apply a \textbf{diverse set of attacks} (especially when training on one attack approach).
  \begin{itemize}[leftmargin=*]
  \item Do not blindly apply multiple (nearly-identical) attack approaches.
  \end{itemize}
\item \S\ref{sec:gradientfree} Try at least one \textbf{gradient-free attack} and one \textbf{hard-label attack}.
  \begin{itemize}[leftmargin=*]
  \item Try \cite{chen2017zoo,uesato2018adversarial,ilyas2018black,brendel2017decision}.
  \item Check that the gradient-free attacks succeed less often than gradient-based attacks.
  \item Carefully investigate attack hyperparameters that affect success rate.
  \end{itemize}
\item \S\ref{sec:transfer} Perform a \textbf{transferability attack} using a similar substitute model.
  \begin{itemize}[leftmargin=*]
    \item Select a substitute model as similar to the defended model as possible.
    \item Generate adversarial examples that are initially assigned high confidence.
    \item Check that the transfer attack succeeds less often than white-box attacks.
  \end{itemize}
\item \S\ref{sec:eot} For randomized defenses, properly \textbf{ensemble over randomness}.
  \begin{itemize}[leftmargin=*]
  \item Verify that attacks succeed if randomness is assigned to one fixed value.
  \item State any assumptions about adversary knowledge of randomness in the threat model.
  \end{itemize}
\item \S\ref{sec:bpda} For non-differentiable components, \textbf{apply differentiable techniques}.
  \begin{itemize}[leftmargin=*]
  \item Discuss why non-differentiable components were necessary.
  \item Verify attacks succeed on undefended model with those non-differentiable components.
  \item Consider applying BPDA~\citep{athalye2018obfuscated} if applicable.
  \end{itemize}
\item \S\ref{sec:converge} Verify that the \textbf{attacks have converged} under the selected hyperparameters.
  \begin{itemize}[leftmargin=*]
  \item Verify that doubling the number of iterations does not increase attack success rate nor significantly change the adversarial loss.
  \item Plot attack effectiveness versus the number of iterations.
  \item Run attacks with multiple random starting points and retain the best one.
  \item Explore different choices of the step size or other attack hyperparameters.
  \end{itemize}
\item \S\ref{sec:hyperparams} Carefully \textbf{investigate attack hyperparameters} and report those selected.
  \begin{itemize}[leftmargin=*]
  \item Start search for adversarial examples at a random offset. Try multiple random starting points for each input.
  \item Investigate if attack results are sensitive to any other hyperparameters.
  \end{itemize}
  \item \S\ref{sec:priorwork} \textbf{Compare against prior work} and explain important differences.
  \begin{itemize}[leftmargin=*]
  \item When contradicting prior work, clearly explain why differences occur.
  \item Attempt attacks that are similar to those that defeated previous similar defenses.
  \item When comparing against prior work, ensure it has not been broken.
  \end{itemize}
\item \S\ref{sec:generalrobustness} Test \textbf{broader threat models} when proposing general defenses. For images:
  \begin{itemize}[leftmargin=*]
  \item Apply rotations and translations \citep{engstrom2017rotation}.
  \item Apply common corruptions and perturbations \citep{hendrycks2018benchmarking}.
  \item Add Gaussian noise of increasingly large standard deviation \citep{ford2019adversarial}.
  \end{itemize}

@@

On at least a few inputs, confirm
that the number of iterations of gradient descent being performed is
sufficient by plotting the attack success and adversarial loss versus the number of
iterations.
%
This plots should eventually plateau; if not, the attack
has not converged and more iterations can be used until
it does. Plotting the adversarial loss is often more useful than plotting the attack success rate, as the former has a finer granularity and thus may reveal that the attack is still making progress even though the success rate seems to have plateaued.
The number of
iterations necessary is generally inversely proportional to step size and
proportional to distortion allowed.
%
Dataset complexity is often related.

@@

There are few reasonable threat models under which an attacker can
compute 100 iterations of gradient descent, but not 1000. As stated in~\cite{athalye2018obfuscated}, merely increasing the time it takes an adversary to find an adversarial example from one second to ten seconds does not constitute an increase in robustness.
%
Because the threat model must not constrain the approach an
attacker takes, it is worth evaluating against a strong attack
with many iterations of gradient descent.

\paragraph{Ensure doubling attack iterations does not increase attack success rate or adversarial loss.}
%
Because choosing any fixed bounded number of iterations can be difficult to
generalize, one simple and useful method for determining if ``enough'' iterations
have been performed is to try doubling the number of iterations and check if this
improves on the adversarial examples generated.
%
This single test is not the only method to select the number of iterations,
but once some value has been selected, doubling the number of iterations
can be a useful test that the number selected is probably sufficient.

@@

\paragraph{Start search from random offsets.}
%
When performing iterative attacks,
it is useful to begin the search for adversarial examples at random
offsets away from the initial, source input.
%
This can reduce the
distortion required to generate adversarial examples by 10\%
\citep{carlini2017towards}, and help avoid causing gradient masking
\citep{tramer2017ensemble,madry2017towards}.
%
Moreover, even if the attack uses sufficient iterations to converge, repeating the attack with multiple randomly chosen starting points decreases the likelihood of ending up in a sub-optimal local minima~\citep{madry2017towards,mosbach2018logit}.
%
Doing this
every time is not necessary, but doing it at least once to verify it
does not significantly change results is worthwhile.
%
Prior work has found that using at least 10 random starting points is effective.

@@

Further ensure that the iterative attack is properly converging, by verifying that increasing the number of iterations or the number of random restarts have no effect on the attack success rate and model loss.
